% =============================================================================
% Tianle Zhang — Curriculum Vitae
% Compile with XeLaTeX (auto-built by GitHub Actions; see .github/workflows/)
% =============================================================================
\documentclass[11pt,a4paper]{article}

% ---------- packages ----------
\usepackage[a4paper,margin=2cm,top=1.8cm,bottom=1.8cm]{geometry}
\usepackage{fontspec}
\usepackage{xeCJK}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}

% ---------- fonts ----------
% Body: Latin Modern (TeX default, available everywhere)
% Chinese: Noto Serif CJK SC (ships with TeX Live full)
\setCJKmainfont[Scale=0.95]{Noto Serif CJK SC}

% ---------- colours ----------
\definecolor{accent}{HTML}{2C5282}
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

% ---------- section style ----------
% All-caps small caps, with full-width rule
\titleformat{\section}
  {\normalfont\large\bfseries\scshape}{}{0em}{}[\vspace{-6pt}\noindent\rule{\linewidth}{0.4pt}]
\titlespacing*{\section}{0pt}{14pt}{4pt}

% ---------- helpers ----------
\newcommand{\me}[1]{\textbf{#1}}                 % self in author lists
\newcommand{\eq}{\textsuperscript{\textbf{*}}}   % equal contribution
\newcommand{\corr}{\textsuperscript{\textbf{\dag}}} % corresponding author

% Two-column entry helpers ----------
% Institution row: bold + suffix, dates right
\newcommand{\entryhead}[3]{%
  \noindent\textbf{#1}#2\hfill #3\par
}
% Sub-row: italic role + advisor, location/date right
\newcommand{\entrysub}[2]{%
  \noindent\textit{#1}\hfill #2\par
}

% Publication entry ----------
% args: {venue tag}{title}{authors}{venue line}
\newcommand{\publication}[4]{%
  \begin{itemize}[leftmargin=1.4em,topsep=2pt,itemsep=0pt,partopsep=0pt]
  \item \textbf{(#1)}~#2.\\
    #3\\
    \textit{In: #4}
  \end{itemize}%
}

% Bulleted lists default
\setlist[itemize]{leftmargin=1.4em, topsep=2pt, itemsep=1pt, partopsep=0pt, parsep=0pt}

\pagestyle{empty}
\setlength{\parindent}{0pt}

% =============================================================================
\begin{document}

% ---------- HEADER ----------
{\Huge\bfseries Tianle Zhang\quad{\normalsize\mdseries (张天乐)}}

\vspace{4pt}
Ph.D.\ Student, College of Computing and Data Science, Nanyang Technological University, Singapore

\vspace{2pt}
\href{mailto:tianle006@e.ntu.edu.sg}{tianle006@e.ntu.edu.sg} \,---\, +65 8491 7566 \,---\,
\href{https://ztlmememe.github.io/}{Homepage} \,---\,
\href{https://scholar.google.com.hk/citations?user=Qbd4ybsAAAAJ&hl=en}{Google Scholar} \,---\, Male

\vspace{2pt}
\textbf{Research interests:}\;
1, \#Multi-modal LLMs \quad
2, \#AI4S \quad
3, \#Efficient Deep Learning \quad
4, \#Evaluation of Generative Models \quad
5, \#Dataset Distillation

% ---------- PROFILE ----------
\section*{Profile}

My research focuses on combining large language models (LLMs) with domain foundation models (FMs) ---
making the integration both efficient and effective --- with growing emphasis on scientific domains
such as small molecules and proteins. On the modeling side, I proposed a training-free framework
that enables LLMs to reason over non-text modalities via in-context representation learning, with
the molecular domain as the testbed (NeurIPS 2025, first author; Prof.\ Alvin Chan as corresponding
author), and contributed to subsequent work on strategic multimodal representation alignment
(AAAI 2026). On the evaluation side, I re-designed the human-evaluation protocol for text-to-video
generation to improve reliability and reproducibility (NeurIPS 2024, first author), and contributed
to ConvBench, a hierarchical multi-turn benchmark for large vision-language models
(NeurIPS 2024 Spotlight). Earlier work on efficient learning includes expanding-window trajectory
matching for lossless graph dataset condensation (ICML 2024, co-first author). Across 8 publications
at top-tier ML venues (NeurIPS, ICML, AAAI) and IEEE conferences, I am first or co-first author on
5. I am supported by the NTU Research Scholarship, and serve as a reviewer for ICLR 2026,
NeurIPS 2025/2026, and ICML 2025/2026. Further details on my
\href{https://ztlmememe.github.io/}{homepage}.

% ---------- EDUCATION ----------
\section*{Education}

\entryhead{Nanyang Technological University}{, College of Computing and Data Science, Singapore}{Jan.~2025 -- Present}
Ph.D.\ in Computer Science;\, Current GPA: 5.0/5.0\\
Advisor: \textit{Prof.\ Alvin Chan Guo Wei} (College of Computing and Data Science, NTU)\\
Funded by \textit{NTU Research Scholarship} (full tuition + stipend; awarded Sep.\ 2024).

\vspace{6pt}
\entryhead{University of Electronic Science and Technology of China}{, Chengdu, China}{Sep.~2020 -- Jun.~2024}
B.Eng.\ in Computer Science and Technology (Joint Degree Program in Smart Finance \& Blockchain Finance)\\
GPA: 88.51/100\\
\textit{Selected coursework:} Machine Learning (97), Data Structures \& Algorithms (95), Smart Contract \& DApps Development (95), Mathematical Modeling (96), Data Mining \& Big Data Analytics (92), Probability \& Statistics (92), Database Theory (91), Software Engineering (91), Computer Organization (90).

% ---------- ACADEMIC EXPERIENCE ----------
\section*{Academic Experience}

\entryhead{Nanyang Technological University}{, College of Computing and Data Science}{Singapore}
\entrysub{Ph.D.\ Student.\, Advisor: Prof.\ Alvin Chan Guo Wei}{Jan.~2025 -- Present}
\begin{itemize}
  \item Exploring new ways to combine large language models (LLMs) with domain foundation models (FMs),
        aiming for integrations that are both more efficient and more effective. Current focus is on
        scientific domains --- small molecules and proteins --- where structured FM representations
        can complement LLM reasoning.
\end{itemize}

\entryhead{Nanyang Technological University}{, College of Computing and Data Science}{Singapore}
\entrysub{Research Assistant.\, Advisor: Prof.\ Alvin Chan Guo Wei}{Oct.~2024 -- Jan.~2025}
\begin{itemize}
  \item Investigated whether large language models can reason over non-text modalities without
        additional training, by treating modality tokens as in-context representations rather than
        fine-tuning targets. The proposed In-Context Representation Learning (ICRL) framework,
        evaluated on the molecular domain, is to our knowledge the first training-free framework
        of its kind. Published at NeurIPS 2025 (first author).
\end{itemize}

\entryhead{Shanghai Artificial Intelligence Laboratory}{}{Shanghai, China}
\entrysub{Trainee Researcher.\, Focus: evaluation of large generative models.}{Oct.~2023 -- Oct.~2024}
\begin{itemize}
  \item Designed the T2VHE protocol, a standardized human-evaluation pipeline for text-to-video
        models with well-defined metrics, annotator training, and a dynamic evaluation module;
        reduces evaluation cost by $\sim$50\% while preserving annotation quality. Published at
        NeurIPS 2024 (first author).
  \item Co-built ConvBench, a hierarchical multi-turn benchmark for large vision-language models
        that disentangles perception, reasoning, and creation. Published at NeurIPS 2024 Spotlight
        (co-author).
\end{itemize}

\entryhead{NUS High Performance Computing for AI (HPC-AI) Lab}{}{Singapore}
\entrysub{Research Intern.\, Focus: graph dataset condensation.}{Apr.~2023 -- Oct.~2024}
\begin{itemize}
  \item Investigated lossless graph dataset condensation. Proposed expanding-window trajectory
        matching with a curriculum-based supervision design that substantially closes the gap to
        full-graph training on large-scale graphs. Published at ICML 2024 (co-first author).
\end{itemize}

% ---------- PUBLICATIONS ----------
\section*{Publications}

\noindent{\small \textbf{Bold} = author of this CV; \textbf{*} = equal contribution; \textbf{\dag} = corresponding author.}

\publication{AAAI'26}
  {To Align or Not to Align: Strategic Multimodal Representation Alignment for Optimal Performance}
  {Wanlong Fang, \me{Tianle Zhang}, Alvin Chan\corr.}
  {Proceedings of the 40th AAAI Conference on Artificial Intelligence, 2026.}

\publication{NeurIPS'25}
  {Can LLMs Reason Over Non-Text Modalities in a Training-Free Manner? A Case Study with In-Context Representation Learning}
  {\me{Tianle Zhang}\eq, Wanlong Fang\eq, Jonathan Woo\eq, Paridhi Latawa, Deepak A. Subramanian, Alvin Chan\corr.}
  {Proceedings of the 39th Conference on Neural Information Processing Systems, 2025.}

\publication{NeurIPS'24}
  {Rethinking Human Evaluation Protocol for Text-to-Video Models: Enhancing Reliability, Reproducibility, and Practicality}
  {\me{Tianle Zhang}, Langtian Ma, Yuchen Yan, Yuchen Zhang, Kai Wang, Yue Yang, Ziyao Guo, Wenqi Shao, Yang You, Yu Qiao, Ping Luo, Kaipeng Zhang\corr.}
  {Proceedings of the 38th Conference on Neural Information Processing Systems, 2024.}

\publication{NeurIPS'24 Spotlight}
  {ConvBench: A Multi-Turn Conversation Evaluation Benchmark with Hierarchical Capability for Large Vision-Language Models}
  {Shuo Liu, Kaining Ying, Hao Zhang, Yue Yang, Yuqi Lin, \me{Tianle Zhang}, Chuanhao Li, Yu Qiao, Ping Luo, Wenqi Shao\corr, Kaipeng Zhang\corr.}
  {Proceedings of the 38th Conference on Neural Information Processing Systems, 2024.}

\publication{ICML'24}
  {Navigating Complexity: Toward Lossless Graph Condensation via Expanding Window Matching}
  {Yuchen Zhang\eq, \me{Tianle Zhang}\eq, Kai Wang, Ziyao Guo, Yuxuan Liang, Xavier Bresson, Wei Jin, Yang You.}
  {Proceedings of the 41st International Conference on Machine Learning, 2024.}

\publication{ICONIP'23}
  {ADGCN: A Weakly Supervised Framework for Anomaly Detection in Social Networks}
  {Zhixiang Shen\eq, \me{Tianle Zhang}\eq\corr, Haolan He\eq.}
  {International Conference on Neural Information Processing, 2023 (CCF-C).}

\publication{IEEE EHB'22}
  {Phase Detection Methods for Alzheimer's Disease Based on Improved Convolutional Neural Network Fine-tuning}
  {\me{Tianle Zhang}, Rui Yin, Zhan Qu, Zhuo Chen.}
  {10th IEEE International Conference on e-Health and Bioengineering, 2022 (IEEE Xplore, SCOPUS, WoS).}

\publication{IEEE ITME'22}
  {Fast Classification of Alzheimer's Disease Based on Improved Convolutional Neural Network}
  {Zhan Qu, \me{Tianle Zhang}, Rui Yin, Zhuo Chen, Teoh Teik Toe.}
  {IEEE International Conference on Information Technology in Medicine and Education, 2022 (IEEE Xplore).}

% ---------- AWARDS ----------
\section*{Awards and Scholarships}

\begin{enumerate}[leftmargin=2em, itemsep=4pt]
  \item \textbf{NTU Research Scholarship (R-RSS)} \hfill Sep.~2024 \\
        \textit{Graduate College, Nanyang Technological University --- full tuition + monthly stipend, awarded for PhD studies.}
  \item \textbf{Excellent First-class Scholarship} \hfill Oct.~2023 \\
        \textit{University of Electronic Science and Technology of China.}
  \item \textbf{Xiaomi Scholarship} \hfill Oct.~2023 \\
        \textit{Xiaomi Foundation $\times$ UESTC.}
  \item \textbf{Tencent First-class Scholarship} \hfill Oct.~2022 \\
        \textit{Tencent Foundation $\times$ UESTC.}
  \item \textbf{NTU Project Scholarship} \hfill Oct.~2022 \\
        \textit{Nanyang Technological University (undergraduate research visit).}
  \item \textbf{Bronze Award, Chengdu 80 Fintech Product R\&D Competition} \hfill Oct.~2021 \\
        \textit{Chengdu Fintech Industry Innovation Center.}
  \item \textbf{Special Prize, 7th UESTC ``Internet Plus'' Innovation \& Entrepreneurship Competition} \hfill Aug.~2021 \\
        \textit{University of Electronic Science and Technology of China.}
  \item \textbf{Second Prize (Sichuan Province), 11th National College Students E-commerce Competition} \hfill Aug.~2021 \\
        \textit{National Ministry of Education.}
  \item \textbf{Blockchain Financial Experiment Class Scholarship} \hfill Oct.~2020 \\
        \textit{University of Electronic Science and Technology of China.}
\end{enumerate}

% ---------- ACADEMIC SERVICE ----------
\section*{Academic Service}

\textbf{Reviewer Recognition}
\begin{itemize}
  \item \textbf{ICML 2026 Gold Reviewer} --- awarded to top reviewers based on area-chair ratings of submitted reviews; includes complimentary conference registration.
\end{itemize}

\textbf{Conference Reviewer}
\begin{itemize}
  \item International Conference on Learning Representations (ICLR): 2026
  \item Conference on Neural Information Processing Systems (NeurIPS): 2025, 2026
  \item International Conference on Machine Learning (ICML): 2025, 2026
  \item ICLR 2025 Workshop on AI for Nucleic Acids (AI4NA)
\end{itemize}

\textbf{Workshop Committee}
\begin{itemize}
  \item ECCV 2024 Workshop on Dataset Distillation Challenge --- Committee Member.
\end{itemize}

% ---------- SKILLS ----------
\section*{Skills and Languages}

\textbf{Programming:} Python (primary), Solidity, C; experienced with DApp / smart-contract development.\\
\textbf{ML / DL:} PyTorch, Hugging Face, scikit-learn; familiar with multi-modal LLMs, diffusion models, GNNs, and dataset distillation pipelines.\\
\textbf{Tools:} Git, Linux, CUDA, LaTeX, Weights \& Biases.\\
\textbf{Languages:} Chinese (Native); English (Fluent --- academic writing, presentation, NeurIPS poster experience).

\end{document}
